Forward Modeling Galaxy Size in a Cosmological Context

### 2017-10-03 paper/galsize_paper.tex
Updated figure 4 caption

In \S\ref{subsec:predictions} we show comparisons between the galaxy size models described in \S\ref{sec:model} and our SDSS sample.

\subsection{Testing Model Predictions}
\label{subsec:predictions}

@@

We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds, $\mstar>10^{9.75}\msun,$ $\mstar>10^{10.25}\msun,$ $\mstar>10^{10.75}\msun,$ and $\mstar>10^{11.25}\msun.$ We make the same measurements for each volume-limited $\mstar-$threshold sample {\em without} splitting on size, giving us measurements $\wpall, \wplarge,$ and $\wpsmall$ for each threshold sample. This allow us to compute the ratio $(\wplarge-\wpsmall)/\wpall,$ which we refer to as {\em the $\rhalf$ clustering ratio}. These ratios are the measurements appearing on the y-axis in each panel of Figure \ref{fig:clustering_ratio_upshot}. Points with error bars show SDSS measurements, solid curves show the clustering ratios of model galaxies as predicted by the models described in \S\ref{sec:model}.

@@

\subsection{Origin of the size-dependence of galaxy clustering}
\label{subsec:shuffle_tests}

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/cen_sat_sizes.pdf}
\caption{
{\bf Relative sizes of centrals and satellites.} In a narrow bin of halo mass $\mhalo=\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies. The red histogram shows the sizes of satellites; the blue histogram shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green histogram host halos that were subhalos inside a larger at some point in their past history (``splashback halos"). In the fiducial model, galaxy size is set by the physical size of the virial radius at the time the (sub)halo attains its peak mass, naturally resulting in smaller sizes for satellites and backsplash centrals relative to true centrals of the same $\mpeak.$
}
\label{fig:censatsizehist}
\end{figure}
%-----------------------------------------------------------------------------------------------------

>>>>

@@

We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds, $\mstar>10^{9.75}\msun,$ $\mstar>10^{10.25}\msun,$ $\mstar>10^{10.75}\msun,$ and $\mstar>10^{11.25}\msun.$ We make the same measurements for each volume-limited $\mstar-$threshold sample {\em without} splitting on size, giving us measurements $\wpall, \wplarge,$ and $\wpsmall$ for each threshold sample. This allow us to compute the ratio $(\wplarge-\wpsmall)/\wpall,$ which we refer to as {\em the $\rhalf$ clustering ratio}. These ratios are the measurements appearing on the y-axis in each panel of Figure \ref{fig:clustering_ratio_upshot}. Points with jackknife-estimated error bars show SDSS measurements, solid curves show the clustering ratios of model galaxies as predicted by the models described in \S\ref{sec:model}.

@@

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/cen_sat_sizes.pdf}
\caption{
{\bf Relative sizes of centrals and satellites.} In a narrow bin of halo mass $\mhalo=\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies, as predicted by the $\rvir-$only model. The red histogram shows the sizes of satellites; the blue histogram shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green histogram host halos that were subhalos inside a larger at some point in their past history (``splashback halos"). In the $\rvir-$only model, galaxy size is set by the {\em physical} size of the virial radius at the time the halo attains its peak mass, naturally resulting in smaller sizes for satellites and backsplash centrals relative to true centrals of the same $\mpeak.$ The central/satellite size differences shown here are not enough to correctly predict the observed clustering ratios (see Figure \ref{fig:clustering_ratio_upshot}), motivating the $\mstar-$stripping and profile co-evolution models. 
}
\label{fig:censatsizehist}
\end{figure}
%-----------------------------------------------------------------------------------------------------
